|

### 2021-05-11 front-and-back-matter/99-appendices.Rmd
End of day: -2625
End of day: -3892

@@

@@

```{r, echo = FALSE}
robvisstats <- cranlogs::cran_downloads("robvis", from = "2019-11-22", to = format(Sys.Date(),"%Y-%m-%d") )

@@

date <- format(Sys.Date(),"%B %Y")

>>>>

### Amendments to protocol {#appendix-cprd-amendments}

@@

## Chapter \@ref(discussion-heading)

### Catalogue of failures

Short section detailing the things I tried to do but which did not work.

@@

```{r, echo = FALSE}
robvisstats <- cranlogs::cran_downloads("robvis", from = "2019-11-22", to = "2021-12-01")

@@

date <- format(as.Date("2021-12-01"),"%B %Y")

### 2021-05-11 index.Rmd
End of day: -3892

```{r create_chunk_options, include=FALSE, eval=knitr::is_latex_output()}
source('scripts_and_filters/create_chunk_options.R')
source("R/helper.R")
```

>>>>

```{r create_chunk_options, include=FALSE, eval=knitr::is_latex_output()}
source('scripts_and_filters/create_chunk_options.R')
source("R/helper.R")
options(scipen=999)
```
